---
title: "Check collected data"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

library(tidyverse)
library(jsonlite)
library(jspsychread)
library(kableExtra)

fn <- here::here("R/data/raw/jatos_results_20220517095331.txt")

stimulus_url_prefix <- "https://stimuly.utia.cas.cz/stimuliData/exp01/"

theme_set(theme_minimal())
upper_limit <- function(x, limit) { x[x>limit] <- limit; x }
kt <- function(x) { kbl(x) %>% kable_paper("hover", full_width = F) }
```

```{r protocols}
n_rep <- 1
set <- paste0(rep(sprintf("%03d", 1:28), each = 2), c("A", "B")) %>% sort()
# conditions <- list(conditions = rep(set, each = n_rep))
```

```{r processing}
d <- read_jspsych(fn, single = F)
n <- length(unique(d$record))

browser <-
  d %>% 
  filter(trial_type == "browser-check", trial_index == 0) %>% 
  unnest_wider(raw)

meta <- 
  d %>% 
  filter(trial_type == "call-function", trial_index == 1) %>% 
  unnest_wider(raw) %>% 
  unnest_wider(value) %>% 
  unnest_wider(params) %>% 
  unnest_wider(opts) %>% 
  unnest_wider(other) %>% 
  select(-(2:5))

video_trials <-
  d %>% 
  filter(trial_type == "video-button-response") %>% 
  mutate(processed = map(raw, ~parse_video_keyboard_response(.x))) %>% 
  unnest(processed)

video_trials <- 
  video_trials %>% 
  mutate(video_long = str_remove_all(stimulus, stimulus_url_prefix),
         video_file = str_remove_all(video_long, "^.*/"),
         video_group = str_remove_all(video_long, "/.*$"), 
         video = str_remove_all(video_file, ".mp4")) %>% 
  group_by(record) %>% 
  mutate(index = 1:n()) %>% ungroup()

vd <- 
  video_trials %>% 
  select(record, index, video_group, video, response, rt)

catch <-
  vd %>% filter(video_group == "catch") %>% 
  separate(video, into = c("orig", "left", "right"), sep = "_", remove = F) %>% 
  mutate(expected = case_when(orig == left ~ 0L, orig == right ~ 1L, T ~ NA_integer_)) %>% 
  mutate(correct = response == expected) %>% 
  left_join(meta %>% select(record, PROLIFIC_PID), by = "record")
```

## Info

This is report based on file: **`r basename(fn)`**

The file contains **N=`r n` records**.

## Time course

```{r}
vd %>% 
  mutate(rt_top = upper_limit(rt, 10), above = rt > 10) %>% 
  left_join(meta %>% select(record, PROLIFIC_PID), by = "record") %>% 
  ggplot(aes(x = index, y = rt, group = record)) + 
  geom_point() + geom_path(aes(colour = PROLIFIC_PID))
```

## Catch trials

```{r}
catch_errors <-
  catch %>% group_by(PROLIFIC_PID) %>% summarise(n_error = sum(!correct))
catch_errors %>% kt()

valid0 <- catch_errors %>% filter(n_error == 0) %>% pull(PROLIFIC_PID)
valid1 <- catch_errors %>% filter(n_error <= 1) %>% pull(PROLIFIC_PID)
```

### Approve

The following people made **no error** in catch trials:

> `r valid0` 

The following people made **max. 1 error** in catch trials:

> `r valid1` 

## Protocols

In this batch we administered the following protocols:

```{r}
meta %>% count(protocol_num) %>% kt()
```

If we accept all people with max. 1 error in catch trials (N=`r length(valid1)`),
the following protocols remain to be administered:

```{r}
used_valid1 <- 
  meta %>% 
  filter(PROLIFIC_PID %in% valid1) %>% 
  count(PROLIFIC_PID, protocol_num) %>% 
  pull(protocol_num)
jsonlite::toJSON(list(conditions = setdiff(rep(set, each = n_rep), used_valid1)))
```

