---
title: "Protocol codes"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(tidyverse)
library(jsonlite)

n_rep <- 1
set <- paste0(rep(sprintf("%03d", 1:28), each = 2), c("A", "B")) %>% sort()
conditions <- list(conditions = rep(set, each = n_rep))
```

The protocol codes in pilot experiment range from `001A` to `028B`. To double check, here are all codes sorted alphabetically 
(total count = **`r length(set)`**).

```{r}
set
```

Each protocol will be administered **`r n_rep``** times.

## How to setup JATOS

1) Open component properties (on righ side, in blue).
2) Paste following code into JSON input field (see below, without `##`)
3) Create a batch (in Study links)
4) Run experiment once (likely to fail but setup the counter)
5) You can use the link for experiments!
6) If you want to check the available protocols in the batch, check Batch session data.

For alternative to Step 4, you can also copy+paste the identical code into the Batch session data.

```{r}
jsonlite::toJSON(conditions)
```

