---
title: "Mulitple regression"
author: "FD"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse); theme_set(theme_minimal(16))
library(here)

raw <- read_table2(here("R/data/EXP1_rating_embedding_10dims_all_101122.txt"), col_names = F) %>% 
  select(-X31) %>% 
  mutate(dimension = rep(1:10, each = 45)) 
df_exp1 <- raw %>% 
  pivot_longer(cols = -dimension, names_to = "material_id", values_to = "rating") %>% 
  arrange(material_id) %>% 
  mutate(rater_id = rep(1:45, times = 300)) %>% 
  group_by(rater_id) %>% 
  mutate(rating_scaled = (rating - mean(rating))/sd(rating) )

rating_names <- tibble(dimension = 1:10, dim_name = c("brightness","glossiness","colourfulness","directionality","complexity","contrast","roughness","patchiness/regularity","line elongation","spatial scale"))
df_exp1 <- df_exp1 %>% left_join(rating_names)


vice <- read_csv(here("R/data/EXP1_VICEembedding_01.csv"),col_names = F) 
colnames(vice) <- paste0("vice",1:9)
vice <- vice %>% 
  mutate(material_id = paste0("X",1:30))

df_exp1_nested <- df_exp1 %>% 
  ungroup() %>% 
  nest_by(dim_name)


df <- df_exp1 %>% 
  group_by(material_id,dim_name) %>% 
  summarize(rating = mean(rating),
            rating_scaled = mean(rating_scaled)) %>% 
  select(material_id, rating, dim_name) %>% 
  pivot_wider(names_from = dim_name, values_from = rating) %>% 
  left_join(vice)

df_scaled <- df_exp1 %>% 
  group_by(material_id,dim_name) %>% 
  summarize(rating = mean(rating),
            rating_scaled = mean(rating_scaled)) %>% 
  select(material_id, rating_scaled, dim_name) %>% 
  pivot_wider(names_from = dim_name, values_from = rating_scaled) %>% 
  left_join(vice)
vice_fit <- function(dfx) {
  lm(value ~ brightness+colourfulness+complexity+contrast+glossiness+directionality+`line elongation` + `patchiness/regularity` + `spatial scale` +  roughness, data = dfx)
}

print_stars <- function(p) {
  ifelse(p < 0.001,"***",
         ifelse(p < 0.01,"**",
                ifelse(p < 0.05,"*","")))
}
```

##  Scatterplots of ratings and vice
I am showing correlation only for VICE with 9 dimensions and rating from video study. This is for first dimension only, but the general patrern in similar for the rest there are low values for some materials 

```{r}

df %>% ggplot(aes(x = brightness, y = vice1)) + geom_point(size = 2) + theme(aspect.ratio = 1)
df %>% ggplot(aes(x = colourfulness, y = vice1)) + geom_point(size = 2) + theme(aspect.ratio = 1)
df %>% ggplot(aes(x = complexity, y = vice1)) + geom_point(size = 2) + theme(aspect.ratio = 1)
df %>% ggplot(aes(x = contrast, y = vice1)) + geom_point(size = 2) + theme(aspect.ratio = 1)
df %>% ggplot(aes(x = directionality, y = vice1)) + geom_point(size = 2) + theme(aspect.ratio = 1)
df %>% ggplot(aes(x = glossiness, y = vice1)) + geom_point(size = 2) + theme(aspect.ratio = 1)
df %>% ggplot(aes(x = `line elongation`, y = vice1)) + geom_point(size = 2) + theme(aspect.ratio = 1)
df %>% ggplot(aes(x = `patchiness/regularity`, y = vice1)) + geom_point(size = 2) + theme(aspect.ratio = 1)
df %>% ggplot(aes(x = roughness, y = vice1)) + geom_point(size = 2) + theme(aspect.ratio = 1)
df %>% ggplot(aes(x = `spatial scale`, y = vice1)) + geom_point(size = 2) + theme(aspect.ratio = 1)
```

## Correlation between rating and vice

Just a quick visual inspection, colourfulness, complexity and contrast seems highly correlated.

```{r}
df %>% ungroup() %>% select(brightness:`spatial scale`,vice1) %>% as.matrix() %>% pairs()
```

### Vice dimensions - raw data

```{r}

df_lm <- df %>% 
  pivot_longer(cols = vice1:vice9,names_to = "vice_dimension") %>% 
  ungroup() %>% 
  nest_by(vice_dimension) %>% 
  mutate(lm_obj = list(vice_fit(data)),
         R2 = (lm_obj %>% summary())$r.squared) %>% 
  mutate(coefs = list(broom::tidy(lm_obj %>% summary)))  %>% 
  unnest(coefs) %>% 
  mutate(est = sprintf("%.2f%s",estimate,print_stars(p.value))) %>% 
  select(vice_dimension:term,est) %>% 
  filter(term != "(Intercept)") %>% 
  pivot_wider(id_cols = vice_dimension:R2,names_from = term, values_from = est) %>% 
  select(-data,-lm_obj)

df_lm %>% 
  knitr::kable(caption = "regression coefficients for videos with raw rating values",digits = 2)

df_lm$R2 %>% mean() %>% round(2)
```

```{r}
library(car)
lm1 <- lm(vice1 ~ brightness+colourfulness+complexity+contrast+glossiness+directionality+`line elongation` + `patchiness/regularity` + `spatial scale` +  roughness, data = df)
vif(lm1)
summary(lm1)
lmx1 <- lm(vice1 ~ brightness+complexity+glossiness+`line elongation` + `spatial scale` +  roughness, data = df)
lmx1 %>% summary()

lmx2 <- lm(vice1 ~ roughness, data = df)
lmx2 %>% summary()
anova(lmx1,lmx2)

lm2 <- lm(vice2 ~ brightness+colourfulness+complexity+contrast+glossiness+directionality+`line elongation` + `patchiness/regularity` + `spatial scale` +  roughness, data = df)
vif(lm1)
summary(lm1)
lm(vice2 ~ brightness+complexity+glossiness+`line elongation` + `spatial scale` +  roughness, data = df) %>% summary()

lm(vice2 ~ complexity+glossiness+`spatial scale` +  roughness, data = df) %>% summary()


lm(vice3 ~ brightness+complexity+glossiness+`line elongation` + `spatial scale` +  roughness, data = df) %>% summary()
lm(vice4 ~ brightness+complexity+glossiness+`line elongation` + `spatial scale` +  roughness, data = df) %>% summary()



```

### Vice dimensions - z-transformed data

```{r}

df_lm_scaled <- df_scaled %>% 
  pivot_longer(cols = vice1:vice9,names_to = "vice_dimension") %>% 
  ungroup() %>% 
  nest_by(vice_dimension) %>% 
  mutate(lm_obj = list(vice_fit(data)),
         R2 = (lm_obj %>% summary())$r.squared) %>% 
  mutate(coefs = list(broom::tidy(lm_obj %>% summary)))  %>% 
  unnest(coefs) %>% 
  mutate(est = sprintf("%.2f%s",estimate,print_stars(p.value))) %>% 
  select(vice_dimension:term,est) %>% 
  filter(term != "(Intercept)") %>% 
  pivot_wider(id_cols = vice_dimension:R2,names_from = term, values_from = est) %>% 
  select(-data,-lm_obj)

df_lm_scaled %>% 
  knitr::kable(caption = "regression coefficients for videos with z-scored values",digits = 2)
```
