---
title: "Simulated sets"
output: html_document
date: "`r format(Sys.time(), '%Y-%m-%d')`"
---

The following code generates a simulated set 
of stimuli and corresponding similarity judgements. 
The stimuli are uniformly distributed in 3D space (intervals (0, 1)) and 
can be imagined as random colours in RGB space.

Notes

- the uniformity is not absolute, we added small amount of noise to avoid identical distances
- similarity is evaluated via the Euclidean distance (of 3D vectors)
- we created several sets with increasing numbers (27, 64, 125, 216), i.e. 3^3, 4^3, 5^3, 6^3

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

library(tidyverse)
library(writexl)

source(here::here("R", "utils_simulation.R"))

theme_set(theme_minimal())

delta <- 0.05
default_distance <- function(n, delta = 0) { (1 - 2 * delta) / (n - 1) }
# how the interval is divided
values <- function(n, delta = 0) {
  tibble(index = 1:n, value = delta + default_distance(n, delta) * (index - 1))
}
cube <- function(vals) {
  crossing(
    vals %>% rename_with(~ str_c(.x, "_1")),
    vals %>% rename_with(~ str_c(.x, "_2")), 
    vals %>% rename_with(~ str_c(.x, "_3"))
  )
}
add_noise_3d <- function(v3, dev) {
  v3 %>% 
    mutate(
      value_1 = value_1 + runif(n(), min = -dev, max = dev),
      value_2 = value_2 + runif(n(), min = -dev, max = dev),
      value_3 = value_3 + runif(n(), min = -dev, max = dev)
    )
}
all_values <- function(d) { c(d$value_1, d$value_2, d$value_3) }

set.seed(42)
stimuli3 <- values(3, delta) %>% cube() %>% add_noise_3d(dev = 0.02) %>% 
  mutate(colour = rgb(value_1, value_2, value_3)) %>% mutate(index = 1:n(), .before = 1)
stimuli4 <- values(4, delta) %>% cube() %>% add_noise_3d(dev = 0.02) %>% 
  mutate(colour = rgb(value_1, value_2, value_3)) %>% mutate(index = 1:n(), .before = 1)
stimuli5 <- values(5, delta) %>% cube() %>% add_noise_3d(dev = 0.02) %>% 
  mutate(colour = rgb(value_1, value_2, value_3)) %>% mutate(index = 1:n(), .before = 1)
stimuli6 <- values(6, delta) %>% cube() %>% add_noise_3d(dev = 0.02) %>% 
  mutate(colour = rgb(value_1, value_2, value_3)) %>% mutate(index = 1:n(), .before = 1)

stopifnot(all_values(stimuli3) < 1)
stopifnot(all_values(stimuli3) > 0)
stopifnot(all_values(stimuli4) < 1)
stopifnot(all_values(stimuli4) > 0)
stopifnot(all_values(stimuli5) < 1)
stopifnot(all_values(stimuli5) > 0)
stopifnot(all_values(stimuli6) < 1)
stopifnot(all_values(stimuli6) > 0)

complete3 <- complete_responses(stimuli3 %>% rename(orig = index))
complete4 <- complete_responses(stimuli4 %>% rename(orig = index))
complete5 <- complete_responses(stimuli5 %>% rename(orig = index))
complete6 <- complete_responses(stimuli6 %>% rename(orig = index))

```

```{r, echo=FALSE, message=FALSE}
system.time(r3 <- complete3 %>% add_distances_vectorized(set = stimuli3 %>% select(starts_with("val"))))
system.time(r4 <- complete4 %>% add_distances_vectorized(set = stimuli4 %>% select(starts_with("val"))))
system.time(r5 <- complete5 %>% add_distances_vectorized(set = stimuli5 %>% select(starts_with("val"))))
system.time(r6 <- complete6 %>% add_distances_vectorized(set = stimuli6 %>% select(starts_with("val"))))
```

```{r}
data_list <- list(
  sim027_responses = r3, sim027_values = stimuli3,
  sim064_responses = r4, sim064_values = stimuli4,
  sim125_responses = r5, sim125_values = stimuli5,
  sim216_responses = r6, sim216_values = stimuli6
)
folder <- here::here("R", "data", "simulated_sets", "balanced")
zipfile <- file.path(folder, "balanced.zip")
if (!dir.exists(folder)) dir.create(folder)

file_list <- names(data_list) %>% map(~ str_c(file.path(folder, .x), ".csv"))
x_ <- map2(data_list, file_list, ~ write_csv(.x, file = .y))
x_ <- file_list %>% map(~ zip(zipfile, .x))
# write_xlsx(
#   data_list, 
#   path = here::here("R", "data", "simulated_sets", "simulated_sets_balanced.xlsx")
# )
```


## MDS on Euclidean distance data

### Set 27

```{r}
d3 <- dist(stimuli3 %>% select(starts_with("val")))
mds3 <- cmdscale(d3, k = 2)

qplot(mds3[, 1], mds3[, 2], colour = stimuli3$colour, size = I(10)) + 
  scale_colour_identity() + 
  labs(x = "MDS dim 1", y = "MDS dim 2", title = "Set with 27 samples")
```

### Set 64

```{r}
d4 <- dist(stimuli4 %>% select(starts_with("val")))
mds4 <- cmdscale(d4, k = 2)

qplot(mds4[, 1], mds4[, 2], colour = stimuli4$colour, size = I(10)) + 
  scale_colour_identity() + 
  labs(x = "MDS dim 1", y = "MDS dim 2", title = "Set with 64 samples")
```

### Set 125

```{r}
d5 <- dist(stimuli5 %>% select(starts_with("val")))
mds5 <- cmdscale(d5, k = 2)

qplot(mds5[, 1], mds5[, 2], colour = stimuli5$colour, size = I(10)) + 
  scale_colour_identity() + 
  labs(x = "MDS dim 1", y = "MDS dim 2", title = "Set with 125 samples")
```

### Set 216

```{r}
d6 <- dist(stimuli6 %>% select(starts_with("val")))
mds6 <- cmdscale(d6, k = 2)

qplot(mds6[, 1], mds6[, 2], colour = stimuli6$colour, size = I(10)) + 
  scale_colour_identity() + 
  labs(x = "MDS dim 1", y = "MDS dim 2", title = "Set with 216 samples")
```

